### 2019-01-05 Sections/QTCP_protocol_stack.tex
Cleaning up comments and ???

As an alternative to checksums, we could borrow the notion of quantum error correction (QEC)\index{Quantum error correction (QEC)} and fault-tolerance\index{Fault-tolerance} from quantum computing theory \cite{???}. Here we encode a quantum state into a (polynomially) larger Hilbert space. \textit{Syndrome measurements}\index{Syndromes!Measurements} on some of the states in this larger space allow us to both detect and correct universal error models, such as depolarisation or dephasing, provided that error rates are within the fault-tolerance threshold of the code being employed.

>>>>

As an alternative to checksums, we could borrow the notion of quantum error correction (QEC)\index{Quantum error correction (QEC)} and fault-tolerance\index{Fault-tolerance} from quantum computing theory. Here we encode a quantum state into a (polynomially) larger Hilbert space. \textit{Syndrome measurements}\index{Syndromes!Measurements} on some of the states in this larger space allow us to both detect and correct universal error models, such as depolarisation or dephasing, provided that error rates are within the fault-tolerance threshold of the code being employed.

### 2019-01-05 Sections/about_the_authors.tex
indexing
Game theory complete
Cleaning up comments and ???

\dropcap{P}{eter Rohde} is an ARC Future Fellow in the Centre for Quantum Software \& Information at the University of Technology Sydney, Australia (UTS:Q$|$SI$\rangle$), and associate member of the Hearne Institute for Theoretical Physics at Louisiana State University. He obtained a Bachelor of Computer Systems Engineering with First Class Honours, and a PhD in theoretical physics at the University of Queensland. He has worked at highly-acclaimed international institutes, including the University of Oxford, University of Queensland, Institute for Molecular Biosciences and Max-Planck Institute for the Science of Light, with over 60 publications and 1,500+ citations in quantum optics, quantum computing, quantum information theory, ecology, and politics. His theoretical proposals have inspired several world-leading experimental efforts, including time-bin encoded \textsc{BosonSampling} and sub-shot-noise limited quantum metrology. In his spare time he is a musician, composer, public speaker, libertarian political activist, charity worker, mountaineer and adrenaline junkie. He regularly speaks at prominent political and scientific outreach events, features in newspaper and magazine articles, and conducts radio interviews. He is a very naughty boy and was expelled from preschool\index{Montessori}.

%
% Heliang Huang
%

%
% Zuen Su
%

@@

@@

@@

>>>>

\dropcap{P}{eter Rohde} is an Australian Research Council Future Fellow in the Centre for Quantum Software \& Information at the University of Technology Sydney, Australia (UTS:Q$|$SI$\rangle$), and associate member of the Hearne Institute for Theoretical Physics at Louisiana State University. He obtained a Bachelor of Computer Systems Engineering with First Class Honours, and a PhD in theoretical physics at the University of Queensland. He has worked at highly-acclaimed international institutes, including the University of Oxford, University of Queensland, Institute for Molecular Biosciences and Max-Planck Institute for the Science of Light, with over 60 publications and 1,500+ citations in quantum optics, quantum computing, quantum information theory, ecology, and politics. His theoretical proposals have inspired several world-leading experimental efforts, including time-bin encoded \textsc{BosonSampling} and sub-shot-noise limited quantum metrology. He is a collaborator in China's world-first quantum satellite program, aiding in the design of quantum protocols for space-based demonstration. xIn his spare time he is a musician, composer, public speaker, libertarian political activist, charity worker, mountaineer, and adrenaline junkie. He regularly speaks at prominent political and scientific outreach events, features in newspaper and magazine articles, and conducts radio and podcast interviews. He is a very naughty boy and was expelled from preschool\index{Montessori}.

@@

%
% He-Liang Huang
%

%
% Zu-en Su
%

@@

%
% Atul Mantri
%

\begin{center}
%\includegraphics[clip=true, width=0.475\textwidth]{photo_atul_mantri}
\end{center}

\dropcap{A}{tul Mantri} is .... \comment{Complete this section}

@@

%
% Scott Harrison
%

\begin{center}
%\includegraphics[clip=true, width=0.475\textwidth]{photo_scott_harrison}
\end{center}

\dropcap{S}{cott Harrison} is ....\comment{Complete this section}

%
% Darryl Veitch
%

\begin{center}
%\includegraphics[clip=true, width=0.475\textwidth]{photo_darryl_veitch}
\end{center}

\dropcap{D}{arryl Veitch} is .....\comment{Complete this section}

### 2019-01-05 Sections/cryptowars.tex
Cleaning up comments and ???

The BB84 protocol has no measurement timing, mode-matching or interferometric stability requirements, making it a very robust protocol, readily achievable with present-day photonics technology. The scheme has been adapted to physical architectures beyond just polarisation-encoded photons, such as CV encodings\index{Continuous-variables!Quantum key distribution (QKD)} \cite{???}.

>>>>

The BB84 protocol has no measurement timing, mode-matching or interferometric stability requirements, making it a very robust protocol, readily achievable with present-day photonics technology. The scheme has been adapted to physical architectures beyond just polarisation-encoded photons, such as CV encodings\index{Continuous-variables!Quantum key distribution (QKD)} (see Sec.~\ref{sec:CV_QKD}).

### 2019-01-05 Sections/encrypted_cloud_quantum_computing.tex
indexing
Cleaning up comments and ???

The difference between the two protocols lies in the treatment of algorithms. In homomorphic encryption, Alice provides only the data, whereas Bob provides the processing and the algorithm it implements (which \comment{in some cases} he would also like to keep to himself). \comment{When any circuit is allowed, the protocol is said to be a {\it fully} homomorphic encryption protocol (FHE). Otherwise, it is a somewhat-homomorphic encryption protocol. \comment{Although homomorphic encryption protocols have been around for a few decades in the form of privacy homomorphisms \cite{bib:Rivest1978}, classical FHE} has only been described very recently \cite{bib:gentry2009fully, bib:van2010fully}.} In blind computing, Alice provides both the algorithm \textit{and} the data, and wishes \textit{both} to remain secret. Both of these protocols seem like very challenging goals, yet significant developments have been made on both fronts \comment{in the quantum world. Interestingly, there are no classical analogue for universal blind computation. Classical FHE will be discussed in the next subsection.}

In the usual circuit model, blind quantum computation has been shown to be viable, and optimal bounds derived. Equivalently, such protocols have been described in the cluster state model (Sec.~\ref{sec:CSQC}). For universal computation, such protocols necessarily require classical interaction between the client and host. However, it was shown that in some restricted (i.e non-universal) models for optical quantum computation, specifically \textsc{BosonSampling}, quantum walks and coherent state passive linear optics, non-interactive \comment{(somewhat-)}homomorphic encryption may be implemented.

@@

In fact, this encryption technique applies to more than just linear optics, but extends to also include generalised non-linear phase-shift operations, generated by Hamiltonians that are polynomials in the photon-number operators,
\begin{align}
\hat{H} = O(\mathrm{poly}(\hat{n}_1,\dots,\hat{n}_m)),
\end{align}
where $\hat{n}_i$ is the photon-number operator for the $i$th mode\index{Photon-number operator}. This observation follows trivially from the observation that the phase-shift encoding operations (which are generated by Hamiltonians linear in the photon-number operators) commute with any polynomial in the photon-number operators,
\begin{align}
[\hat{n}_i,\mathrm{poly}(\hat{n}_1,\dots,\hat{n}_m)] = 0\,\,\forall \, i.
\end{align}
This immediately significantly expands the class of operations available for the computation. In particular, while coherent states remain separable under linear optics evolution, the introduction of non-linear phase-shift operations enables quantum entanglement, and presumably a more powerful class of computations than simple matrix multiplication. It is unclear to us, however, exactly what this class of computations actually is.

>>>>

The difference between the two protocols lies in the treatment of algorithms:
\begin{itemize}
	\item Homomorphic encryption: Alice provides only the data, whereas Bob provides the processing and the algorithm it implements (which he would also like to keep to himself in general). When \textit{any} circuit is allowed, the protocol is said to be a \textit{fully homomorphic} encryption protocol (FHE). Otherwise, it is a \textit{somewhat-homomorphic} encryption protocol. Although homomorphic encryption protocols have been around for a few decades in the form of privacy homomorphisms \cite{bib:Rivest1978}, classical FHE has only been described very recently \cite{bib:gentry2009fully, bib:van2010fully}.
	\item Blind quantum computing: Alice provides both the algorithm \textit{and} the data, and wishes \textit{both} to remain secret to her. It is known that universal blind \textit{classical} computation is not possible, universal blind \textit{quantum} computation is.
\end{itemize}
Both of these seem like very challenging goals, yet significant developments have been made on both fronts in the quantum world, with efficient resource overheads associated with the encryption.

In the usual circuit model, blind quantum computation has been shown to be viable, and optimal bounds derived. Equivalently, such protocols have been described in the cluster state model (Sec.~\ref{sec:CSQC}). For universal computation, such protocols necessarily require classical interaction between the client and host. However, it was shown that in some restricted (i.e non-universal) models for optical quantum computation, specifically \textsc{BosonSampling}, quantum walks and coherent state passive linear optics, non-interactive, somewhat-homomorphic encryption may be implemented.

@@

In fact, this encryption technique applies to more than just linear optics, but extends to also include generalised non-linear phase-shift operations, generated by Hamiltonians that are polynomials in the photon-number operators,
\begin{align}
\hat{H} = O(\mathrm{poly}(\hat{n}_1,\dots,\hat{n}_m)),
\end{align}
where $\hat{n}_i$ is the photon-number operator for the $i$th mode\index{Photon-number!Operators}. This observation follows trivially from the observation that the phase-shift encoding operations (which are generated by Hamiltonians linear in the photon-number operators) commute with any polynomial in the photon-number operators,
\begin{align}
[\hat{n}_i,\mathrm{poly}(\hat{n}_1,\dots,\hat{n}_m)] = 0\,\,\forall \, i.
\end{align}
This immediately significantly expands the class of operations available for the computation. In particular, while coherent states remain separable under linear optics evolution, the introduction of non-linear phase-shift operations enables quantum entanglement, and presumably a more powerful class of computations than simple matrix multiplication. It is unclear to us, however, exactly what this class of computations actually is.

### 2019-01-05 Sections/entanglement_the_ultimate_quantum_resource.tex
Cleaning up comments and ???

What's the advantage of this approach to quantum networking? Why specialise in entanglement distribution, rather than implementing more capable networks with the ability to perform arbitrary operations? There are numerous:
\begin{enumerate}
\item Dedicated servers can specialise in this one particular task, as can be the transmission infrastructure.
\item The entanglement servers are entirely passive, not involved interactively with clients.
\item The server needn't concern itself with the nitty-gritty of the protocols implemented by the end-user. It acts purely as a provider of a single resource, remaining uninvolved in their subsequent applications.
\item Because servers are providing a single standardised product, they can be commodified, enabling mass production of the hardware devices and the associated economy of scale. For example, mass production of simple ground-based Bell state relays, or the construction of a comprehensive globe-enveloping constellation of satellites, would inevitably improve economies of scale.
\item Unlike generic quantum states, Bell pairs, GHZ states and cluster states are known states that are infinitely reproducible, without having to worry about no-cloning\index{No-cloning theorem} limitations.
\item Photonic Bell pairs are easily prepared via type-II SPDC at very high repetition rates (\mbox{$\sim 100$MHz-1GHz}), enabling rapid state preparation.
\item Small entangled states like Bell pairs are relatively `cheap' to prepare, and can be readily manufactured using widely accessible, present-day technology that has already been well-demonstrated on Earth and in space \cite{???}.
\item QoS is a lesser issue in most scenarios. We can employ a \textsc{Send-and-forget}\index{Send-and-forget strategy} protocol for the distribution of entanglement (much like classical UDP\index{User Datagram Protocol (UDP)}) -- since every state is identical, we needn't be concerned about missing ones. Instead, we can simply wait for the next one (a \textsc{Repeat-until-success}\index{Repeat-until-success strategy} strategy), knowing it will be exactly the same. We also call this the \textsc{Shotgun}\index{Shotgun!State preparation} approach -- keep firing away until we hit something, and if we lose a few, who cares?
\item Rather than transmitting quantum states between distant parties directly, if we instead use state teleportation (Sec.~\ref{sec:teleport}) mediated by Bell states, the state to be transmitted will not be corrupted if the communications channel fails (e.g via loss). Instead we can wait for the next successfully transmitted Bell pair until we are ready to teleport the state, which then proceeds without directly utilising the quantum communications channel, accumulating its associated costs, or risking losing the state altogether should link failure occur. Only classical communication is required to complete the protocol, which can be regarded as error-free for all intents and purposes.
\item Entanglement purification may be employed by parties to improve the cost metrics associated with their shared entanglement, thereby partially overcoming the limitations imposed by the quantum communication channels.
\item If no direct link exists between server and clients, bootstrapped entanglement swapping can be employed to concatenate servers to create longer-distance `virtual' links. This is the basis for \textit{quantum repeater networks}, to be discussed next in Sec.~\ref{sec:rep_net}.
\end{enumerate}

>>>>

What's the advantage of this approach to quantum networking? Why specialise in entanglement distribution, rather than implementing more capable networks with the ability to perform arbitrary operations? There are numerous:
\begin{enumerate}
\item Dedicated servers can specialise in this one particular task, as can be the transmission infrastructure.
\item The entanglement servers are entirely passive, not involved interactively with clients.
\item The server needn't concern itself with the nitty-gritty of the protocols implemented by the end-user. It acts purely as a provider of a single resource, remaining uninvolved in their subsequent applications.
\item Because servers are providing a single standardised product, they can be commodified, enabling mass production of the hardware devices and the associated economy of scale. For example, mass production of simple ground-based Bell state relays, or the construction of a comprehensive globe-enveloping constellation of satellites, would inevitably improve economies of scale.
\item Unlike generic quantum states, Bell pairs, GHZ states and cluster states are known states that are infinitely reproducible, without having to worry about no-cloning\index{No-cloning theorem} limitations.
\item Photonic Bell pairs are easily prepared via type-II SPDC at very high repetition rates (\mbox{$\sim 100$MHz-1GHz}), enabling rapid state preparation.
\item Small entangled states like Bell pairs are relatively `cheap' to prepare, and can be readily manufactured using widely accessible, present-day technology that has already been well-demonstrated on Earth and in space.
\item QoS is a lesser issue in most scenarios. We can employ a \textsc{Send-and-forget}\index{Send-and-forget strategy} protocol for the distribution of entanglement (much like classical UDP\index{User Datagram Protocol (UDP)}) -- since every state is identical, we needn't be concerned about missing ones. Instead, we can simply wait for the next one (a \textsc{Repeat-until-success}\index{Repeat-until-success strategy} strategy), knowing it will be exactly the same. We also call this the \textsc{Shotgun}\index{Shotgun!State preparation} approach -- keep firing away until we hit something, and if we lose a few, who cares?
\item Rather than transmitting quantum states between distant parties directly, if we instead use state teleportation (Sec.~\ref{sec:teleport}) mediated by Bell states, the state to be transmitted will not be corrupted if the communications channel fails (e.g via loss). Instead we can wait for the next successfully transmitted Bell pair until we are ready to teleport the state, which then proceeds without directly utilising the quantum communications channel, accumulating its associated costs, or risking losing the state altogether should link failure occur. Only classical communication is required to complete the protocol, which can be regarded as error-free for all intents and purposes.
\item Entanglement purification may be employed by parties to improve the cost metrics associated with their shared entanglement, thereby partially overcoming the limitations imposed by the quantum communication channels.
\item If no direct link exists between server and clients, bootstrapped entanglement swapping can be employed to concatenate servers to create longer-distance `virtual' links. This is the basis for \textit{quantum repeater networks}, to be discussed next in Sec.~\ref{sec:rep_net}.
\end{enumerate}

### 2019-01-05 Sections/models_for_quantum_computation.tex
Cleaning up comments and ???

%
% Adiabatic Quantum Computation & Quantum Annealing
%

\subsection{Adiabatic quantum computation \& quantum annealing} \label{sec:adiabatic_QC} \index{Adiabatic!Quantum computation} \index{Quantum annealing}

@@

In the circuit model, the cost of the computation is equated with the number of gates. In AQC, the cost of adiabatic algorithms is defined to be the dimensionless quantity \cite{bib:aharonov2008adiabatic},
\begin{align}
\mathrm{cost} = t_f \cdot \mathrm{max}_s ||\hat{H}(s)||,
\end{align}
where $t_f$ is the algorithmic runtime, and $||\cdot||$ denotes the operator norm\index{Operator norm}, which is the largest singular value\index{Singular value} of the operator.

The runtime $t_f$ of an adiabatic algorithm scales at worst as \mbox{$O(1/\Delta^3)$}, where $\Delta^3$ is the minimum eigenvalue gap between the ground state and the first excited state of the Hamiltonian \cite{bib:jansen2007bounds} This is the reason why AQC has generated much interest -- it has a rich connection to the well-studied field of condensed matter physics\index{Condensed matter physics}.

@@

% 
These include:
\begin{itemize}
\item The adiabatic Grover algorithm\index{Adiabatic!Grover algorithm}: as its name suggests, this is the adiabatic version of Grover's search algorithm. The initial Hamiltonian is,
\begin{align}
	\hat{H}_0 = \hat\openone - \ket{\phi}\bra{\phi},
\end{align}
where $\ket{\phi}$ is the uniform superposition state $\ket{+}^{\otimes n}$. The final Hamiltonian is given by,
\begin{align}
\hat{H}_1 = \hat\openone - \ket{m}\bra{m},
\end{align}
where $\ket{m}$ is the marked item we are searching for \cite{bib:PhysRevA.65.042308}.
% 
% 
\item The adiabatic Deutsch-Jozsa algorithm\index{Adiabatic!Deutsch-Jozsa algorithm}\index{Deutsch-Jozsa algorithm}: given a binary function,
\begin{align}
f:\{0,1 \}^n \rightarrow \{0,1\},
\end{align}
which is either constant\index{Constant functions} or balanced\index{Balanced functions}, the Deutsch-Jozsa algorithm can determine which type of function it is, exhibiting quantum speedup. An adiabatic implementation \cite{bib:PhysRevLett.95.250503} is derived to match the speedup obtained in the original circuit model implementation.
% 
% 
\item The adiabatic glued-trees problem\index{Adiabatic!Glued-trees problem}: we consider two binary trees\index{Binary trees} of depth $n$. Each tree has \mbox{$2^{n+1}-1$} vertices, and the two trees are randomly glued together, as shown in Fig.~\ref{fig:glued_trees}. A leaf is chosen from the left, connected to a random leaf on the right, which is in turn glued to another leaf on the left and so on. Every leaf on is connected to two on the other side, creating a random cycle that alternates between the two trees.
% 
 The computation problem is to start from the left root and find a path to the right root in the smallest possible number of steps, given that one can only see adjacent vertices. Classical algorithms require at least a sub-exponential number of queries, but there exists a polynomial-time quantum algorithm based on quantum walks \cite{bib:childs2003exponential}.
% 
 % 
\item The adiabatic \textsc{PageRank} algorithm\index{Adiabatic!PageRank algorithm}: the \textsc{PageRank}\index{PageRank algorithm} vector is a crucial tool in data mining and information retrieval, employed heavily by the Google search engine. The goal of the algorithm is to rank the importance, impact or influence of some entity in a network (webpages on the internet in the case of a Google search). The algorithm achieves this by representing the network as a flow network\index{Flow networks}, whereby flow from one vertex to another represents a vote by the source vertex for the importance of the destination vertex. By finding a steady-state flow to each edge in the network, the net flow into vertices represents their cumulative importance, as determined collectively by participants in the network. However, the magnitude of votes cast by vertices is weighted by their own ranking. Therefore, the algorithm aims to filter out bogus gaming of the system via the creation of dummy nodes that cast votes en masse to rig the election. The \textsc{PageRank} approach to ranking webpages has been by far the most successful and robust such algorithm, and was perhaps the key development behind the global success of Google. The best-known classical algorithms for solving the \textsc{PageRank} problem are via: representing the flow network as a matrix equation, from which the solution is obtained via solving an eigenvalue equation; representing the flow network as a random walk, whereby walkers randomly follow paths influenced by the flows, which in the long-time limit yields walks approximating the solution. The current best-known quantum \textsc{PageRank} algorithm outperforms all currently known classical algorithms with polynomial or even exponential speedup \cite{bib:PhysRevLett.108.230506}, but better future classical algorithms have not been ruled out and are under active investigation.
\end{itemize}

@@

If we have in the circuit model an $n$-partical pure state $\ket{\psi}$, acted upon by $U$ with depth $L$, a time-dependent Hamiltonian $\hat{H}(t)$ is universal if:
\begin{itemize}
\item The ground state of $\hat{H}(t_f)$ is equal to $\hat{U}\ket{\psi}$ with non-zero probability.
\item The number of particles in $H(t_f)$ is polynomial in $n$ and $L$, and $t_f$ is also polynomial in $n$ and $L$.
\end{itemize}
It has been proven that AQC can efficiently simulate the entire circuit model \cite{bib:RevModPhys.90.015002}, which implies that it is itself universal for efficient quantum computing.

>>>>

%
% Adiabatic Quantum Computation
%

\subsection{Adiabatic quantum computation} \label{sec:adiabatic_QC} \index{Adiabatic!Quantum computation}

@@

In the circuit model, the cost of the computation is equated with the number of gates. In AQC, the cost of adiabatic algorithms is defined to be the dimensionless quantity \cite{bib:aharonov2008adiabatic},
\begin{align}
\mathrm{cost} = t_f \cdot \mathrm{max}_s ||\hat{H}(s)||,
\end{align}
where $t_f$ is the algorithmic runtime, and $||\cdot||$ denotes the operator norm\index{Operator norm}, the largest singular value\index{Singular value} of the operator.

The worst-case runtime of an adiabatic algorithm scales as,
\begin{align}
t_f = O\left(\frac{1}{\Delta^{(3)}}\right), 
\end{align}
where $\Delta^{(3)}$ is the minimum eigenvalue gap between the ground state and the first excited state of the Hamiltonian \cite{bib:jansen2007bounds}. This is the reason why AQC has generated much interest -- it has a rich connection to the well-studied field of condensed matter physics\index{Condensed matter physics}.

@@

Some of the well-known examples of AQC algorithms\index{Adiabatic!Algorithms} include:
\begin{itemize}
\item Adiabatic Grover algorithm\index{Adiabatic!Grover algorithm}: as its name suggests, this is the adiabatic version of Grover's search algorithm. The initial Hamiltonian is,
\begin{align}
	\hat{H}_0 = \hat\openone - \ket{\phi}\bra{\phi},
\end{align}
where $\ket{\phi}$ is the uniform superposition state $\ket{+}^{\otimes n}$. The final Hamiltonian is given by,
\begin{align}
\hat{H}_1 = \hat\openone - \ket{m}\bra{m},
\end{align}
where $\ket{m}$ is the marked item we are searching for \cite{bib:PhysRevA.65.042308}.
% 
% 
\item Adiabatic Deutsch-Jozsa algorithm\index{Adiabatic!Deutsch-Jozsa algorithm}\index{Deutsch-Jozsa algorithm}: given a binary function,
\begin{align}
f:\{0,1 \}^n \rightarrow \{0,1\},
\end{align}
which is either constant\index{Constant functions} or balanced\index{Balanced functions}, the Deutsch-Jozsa algorithm can determine which type of function it is, exhibiting quantum speedup. An adiabatic implementation \cite{bib:PhysRevLett.95.250503} is derived to match the speedup obtained in the original circuit model implementation.
% 
% 
\item Adiabatic glued-trees problem\index{Adiabatic!Glued-trees problem}: we consider two binary trees\index{Binary trees} of depth $n$. Each tree has \mbox{$2^{n+1}-1$} vertices, and the two trees are randomly glued together, as shown in Fig.~\ref{fig:glued_trees}. A leaf is chosen from the left, connected to a random leaf on the right, which is in turn glued to another leaf on the left and so on. Every leaf on is connected to two on the other side, creating a random cycle that alternates between the two trees.
% 
 The computation problem is to start from the left root and find a path to the right root in the smallest possible number of steps, given that one can only see adjacent vertices. Classical algorithms require at least a sub-exponential number of queries, but there exists a polynomial-time quantum algorithm based on quantum walks \cite{bib:childs2003exponential}.
% 
 % 
\item Adiabatic \textsc{PageRank} algorithm\index{Adiabatic!PageRank algorithm}: the \textsc{PageRank}\index{PageRank algorithm} vector is a crucial tool in data mining and information retrieval, employed heavily by the Google search engine. The goal of the algorithm is to rank the importance, impact or influence of some entity in a network (webpages on the internet in the case of a Google search). The algorithm achieves this by representing the network as a flow network\index{Flow networks}, whereby flow from one vertex to another represents a vote by the source vertex for the importance of the destination vertex. By finding a steady-state flow to each edge in the network, the net flow into vertices represents their cumulative importance, as determined collectively by participants in the network. However, the magnitude of votes cast by vertices is weighted by their own ranking. Therefore, the algorithm aims to filter out bogus gaming of the system via the creation of dummy nodes that cast votes en masse to rig the election. The \textsc{PageRank} approach to ranking webpages has been by far the most successful and robust such algorithm, and was perhaps the key development behind the global success of Google. The best-known classical algorithms for solving the \textsc{PageRank} problem are via: representing the flow network as a matrix equation, from which the solution is obtained via solving an eigenvalue equation; representing the flow network as a random walk, whereby walkers randomly follow paths influenced by the flows, which in the long-time limit yields walks approximating the solution. The current best-known quantum \textsc{PageRank} algorithm outperforms all currently known classical algorithms with polynomial or even exponential speedup \cite{bib:PhysRevLett.108.230506}, but better future classical algorithms have not been ruled out and are under active investigation.
\end{itemize}

@@

If we have in the circuit model an $n$-particle pure state $\ket{\psi}$, acted upon by unitary $\hat{U}$ with circuit depth\index{Circuit depth} $L$, a time-dependent Hamiltonian $\hat{H}(t)$ is universal if:
\begin{itemize}
\item The ground state of $\hat{H}(t_f)$ is equal to $\hat{U}\ket{\psi}$ with non-zero probability.
\item The number of particles in $\hat{H}(t_f)$ is polynomial in $n$ and $L$, and $t_f$ is also polynomial in $n$ and $L$.
\end{itemize}
It has been proven that AQC can efficiently simulate the entire circuit model \cite{bib:RevModPhys.90.015002}, which implies that it is itself universal for efficient quantum computation.

### 2019-01-05 Sections/protocols_for_the_quantum_internet.tex
Cleaning up comments and ???

Transitioning from heralded state preparation to quasi-deterministic state preparation may then be achieved by operating a bank of such sources in parallel, and multiplexing their outputs, such that when all sources are triggered simultaneously, if any one succeeds, the respective single photon is routed to the desired output mode \cite{???}, as shown in Fig.~\ref{fig:SPDC_multiplexing_arch}.

@@

Linear optics networks \cite{bib:TanRohdeRev} implement unitary linear maps on the photonic creation operators, of the form,
\begin{align} \label{eq:LO_unitary_map}
\hat{U}\hat{a}_i^\dag \hat{U}^\dag \to \sum_{j=1}^m U_{i,j} \hat{a}^\dag_j,
\end{align}
where $\hat{a}^\dag_i$ is the photonic creation operator on the $i$th of the $m$ modes, and $U$ may be any $\mathrm{SU}(m)$ matrix. It was shown by \cite{bib:Reck94} that arbitrary transformations of this form may be decomposed into $O(m^2)$ linear optical elements (beamsplitters and phase-shifters), enabling efficient construction of arbitrary linear transformations.\index{Linear optics!Decompositions} Furthermore, the algorithm for determining the decomposition of such transformations has polynomial classical runtime (i.e residing in \textbf{P}\index{P}). Note that the original Reck \textit{et al.} decomposition is not unique, and various other topologies of optical elements also enable universality \cite{???}, each with their own implementational advantages and disadvantages.

@@

Entangled states, most notably Bell pairs (Sec.~\ref{sec:bell_state_res}), play a central role in many quantum technologies. These maximally entangled states are easily represented optically using polarisation encoding of single photons, and can be non-deterministically prepared directly using SPDC (Sec.~\ref{sec:single_phot_src}), or post-selected linear optics \cite{???}.

@@

Quantum state teleportation \cite{???, bib:PRL_70_1895} is an essential ingredient in many higher-level protocols. It forms the basis of cluster state quantum computing (Sec.~\ref{sec:CSQC}), some QEC codes, the KLM linear optics quantum computing scheme (Sec.~\ref{sec:KLM_univ}), and can act as a mediator for long-range transmission of quantum states, amongst others.

@@

The obvious approach to sending a qubit from Alice to Bob is to send a qubit from Alice to Bob (duh!). However, over long distances this may accrue impractical error rates, particularly losses. The other alternative is to employ the quantum state teleportation protocol (Sec.~\ref{sec:teleport}) to teleport the state between the two parties. However, this requires that Alice and Bob first share an entangled Bell pair, which must itself be distributed across the same distances. Entanglement swapping \cite{???, bib:PhysRevLett.75.4337} is the process of taking two Bell pairs, one held by each party, and swapping the entanglement between them such that the two parties share an entangled state. This procedure can be bootstrapped to progressively swap the entanglement over longer and longer distances, yielding \textit{quantum repeater networks} (Sec.~\ref{sec:rep_net}). The procedure for this protocol is shown in Alg.~\ref{alg:ent_swap} and Fig.~\ref{fig:ent_swap}

>>>>

Transitioning from heralded state preparation to quasi-deterministic state preparation may then be achieved by operating a bank of such sources in parallel, and multiplexing their outputs, such that when all sources are triggered simultaneously, if any one succeeds, the respective single photon is routed to the desired output mode, as shown in Fig.~\ref{fig:SPDC_multiplexing_arch}.

@@

Linear optics networks \cite{bib:TanRohdeRev} implement unitary linear maps on the photonic creation operators, of the form,
\begin{align} \label{eq:LO_unitary_map}
\hat{U}\hat{a}_i^\dag \hat{U}^\dag \to \sum_{j=1}^m U_{i,j} \hat{a}^\dag_j,
\end{align}
where $\hat{a}^\dag_i$ is the photonic creation operator on the $i$th of the $m$ modes, and $U$ may be any $\mathrm{SU}(m)$ matrix. It was shown by \cite{bib:Reck94} that arbitrary transformations of this form may be decomposed into $O(m^2)$ linear optical elements (beamsplitters and phase-shifters), enabling efficient construction of arbitrary linear transformations.\index{Linear optics!Decompositions} Furthermore, the algorithm for determining the decomposition of such transformations has polynomial classical runtime (i.e residing in \textbf{P}\index{P}). Note that the original Reck \textit{et al.} decomposition is not unique, and various other topologies of optical elements also enable universality, each with their own implementational advantages and disadvantages.

@@

Entangled states, most notably Bell pairs (Sec.~\ref{sec:bell_state_res}), play a central role in many quantum technologies. These maximally entangled states are easily represented optically using polarisation encoding of single photons, and can be non-deterministically prepared directly using SPDC (Sec.~\ref{sec:single_phot_src}), or post-selected linear optics.

@@

Quantum state teleportation \cite{bib:PRL_70_1895} is an essential ingredient in many higher-level protocols. It forms the basis of cluster state quantum computing (Sec.~\ref{sec:CSQC}), some QEC codes, the KLM linear optics quantum computing scheme (Sec.~\ref{sec:KLM_univ}), and can act as a mediator for long-range transmission of quantum states, amongst others.

@@

The obvious approach to sending a qubit from Alice to Bob is to send a qubit from Alice to Bob (duh!). However, over long distances this may accrue impractical error rates, particularly losses. The other alternative is to employ the quantum state teleportation protocol (Sec.~\ref{sec:teleport}) to teleport the state between the two parties. However, this requires that Alice and Bob first share an entangled Bell pair, which must itself be distributed across the same distances. Entanglement swapping \cite{bib:PhysRevLett.75.4337} is the process of taking two Bell pairs, one held by each party, and swapping the entanglement between them such that the two parties share an entangled state. This procedure can be bootstrapped to progressively swap the entanglement over longer and longer distances, yielding \textit{quantum repeater networks} (Sec.~\ref{sec:rep_net}). The procedure for this protocol is shown in Alg.~\ref{alg:ent_swap} and Fig.~\ref{fig:ent_swap}

### 2019-01-05 Sections/quantum_channels.tex
Cleaning up comments and ???

Treating a link or node as an unknown black box, \textit{quantum process tomography} (QPT) \cite{bib:ChuangNielsen97, ???} is a technique that may be applied to fully characterise the quantum process it implements, reproducing its complete process matrix. QPT has become a standard procedure, demonstrated in numerous architectures, most notably in optics \cite{bib:OBrien04, bib:RohdeGateChar05}.

@@

In the case of optical systems, entirely alternate, but equivalent, approaches may be used, such a probing the Wigner function directly using homodyne detection \cite{???}\index{Homodyne detection}.

>>>>

Treating a link or node as an unknown black box, \textit{quantum process tomography} (QPT) \cite{bib:ChuangNielsen97} is a technique that may be applied to fully characterise the quantum process it implements, reproducing its complete process matrix. QPT has become a standard procedure, demonstrated in numerous architectures, most notably in optics \cite{bib:OBrien04, bib:RohdeGateChar05}.

@@

In the case of optical systems, entirely alternate, but equivalent, approaches may be used, such a probing the Wigner function directly using homodyne detection\index{Homodyne detection}.
